Answers to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-17 cover_letter.tex
Fixed wrong section reference in cover letter
Removed link to YouTube video

A recent video showing the current state of the interaction can be viewed
here: \url{http://www.youtube.com/watch?v=IODx50uV_k4}

@@

{\tt GenerateDescription} translates the parsing tree of each nominal group
into statements. A set of rules (like the one for adjectives mentioned 
in footnote, section 5.1) help with this task. The detailed algorithm is provided in appendix to this letter.  We would be happy to add it to the paper as well if the editor wants to consider it.

>>>>

@@

{\tt GenerateDescription} translates the parsing tree of each nominal group
into statements. A set of rules (like the one for adjectives mentioned 
in footnote, section 4.1) help with this task. The detailed algorithm is provided in appendix to this letter.  We would be happy to add it to the paper as well if the editor wants to consider it.
